Exploration in Target Speaker Extraction using Discrete Representations \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-02 src/paper.tex
update

\title{Exploration in Target Speaker Extraction using Discrete Tokens and Language Models\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. The separation

>>>>

\title{Exploration in Target Speaker Extraction using Discrete Representations 
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

Unlike blind speech separation, which focuses on separating each utterance from a mixture 
of known speakers, target speaker extraction aims at only extracting the 
target speaker's voice given another auxiliary information of the target speaker. Due to the 
development of Deep Neural Network (DNN), many models nowadays are discriminative models. They 
utilize a masking strategy to minimize the distance between the clean speech and estimated 
speech directly \cite{luo2019conv,spex_plus,sepformer,sef_net}. However, these discriminative 
models may not generalize well to unseen data and might even introduce unwanted distortions \cite{distortion}.
